---
title: "Dazzling Reports"
author: "Lindsey Dietz, PhD"
date: "R-Ladies Twin Cities (March 18, 2021)"
output:
  revealjs::revealjs_presentation:
    theme: black
    highlight: monochrome
    transition: fade

---

## Goal of this talk

Introduce tools that help you tell a data story in a professional, sustainable, and beautiful way

## Older process

- Do analysis in one tool (R)
- Make tables and charts in another tool (Excel)
- Paste everything into a text editor (Word)
- Turn it into a final product (PDF)

It works, but doesn't set you up for next time.

## Sustainable process

Build an R ecosystem for everything

- `rmarkdown` is the wrapper
- Table building using `DT` or `reactable` (or others)
- Plotting using `ggplot2` or `plotly`

## R Markdown

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

- Header
- Code chunks
- Markdown/LaTeX

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

<style type="text/css">
  .reveal p {
    text-align: left;
  }
  .reveal ul {
    display: block;
  }
  .reveal ol {
    display: block;
  }  
</style>